### 2021-07-04 rad-icfp-2021/purerad.tex
adding more examples

\begin{example}
    The gradient of the terms from the introduction is

    \begin{tabular}{c r}
        & $\grad_\Gamma$(!let w1 = x1 * x2 in let w2 = w1 * x1 in w2!) \\
        =& TODO \\
        \\
        $\grad_\Gamma$(!prod(A)!) \\
        =& \\
    \end{tabular}
\end{example}

@@

Now, importantly, every !yi! is used at most once (except for !map2! again and !reduce! which require a more detailed analysis)
which garantees that this will not blow up the complexity.

TODO: finish explanation, not sure how to conclude at the moment

@@

TODO: use the optimizations to be efficient on examples

>>>>

@@

TODO: finish explanation

\begin{example}
    The gradient of the terms from the introduction reduces to

    \begin{tabular}{c l}
        & $\grad_\Gamma$(!let w1 = x1 * x2 in let w2 = w1 * x1 in w2!) \\
        =& TODO \\
    \end{tabular}
    \medskip

    \begin{tabular}{c l}
        & $\grad_\Gamma$(!prod(A)!) \\
        =& TODO \\
    \end{tabular}
\end{example}

@@

\begin{example}
As shown in appendix \ref{sub:gradintro}, the optimizations from Figure~\ref{fig:optim} 
are sufficient to show that the gradients of the terms of the introduction reduce to the following.

\begin{tabular}{{r c l}}
    $\nabla_A$!prod(A)! &:=& !map2 * (scanr * 1 A) (shift1(scanl * 1 A))!\\
    $\nabla_A$!sum(A)! &:=& !map (x -> 1) A!\\
    $\nabla_A$!dot(A,B)! &:=& !B! 
\end{tabular}
\end{example}
